---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---
* save this flex_dashboard file in our desktop
  * if i drag this file to desktop, plots ans everything looks great. but if it is in my repository, it looks bad when knitting it.
  * b/c in the repo, our rmd will create a html file when knitting, so things in this file will be overwritten by the _site.html
    * To address this issue, instead of knitting, we can use this command to knit the dashboard: **rmarkdown::render("dashboard.Rmd", output_format = "flexdashboard::flex_dashboard")**. Make sure the output_format is correct. *do this in 'Console'!!*
    * This will create dashboard.html but not open it in RStudio’s Viewer pane;  you can open the file in a browser instead. Alternatively, using RStudio’s Build pane to Build Website will produce the same results. 
* **Column {data-width=}** can control the relative width of our columns of charts
* we can embed interactive graphics in HTML files produced by R Markdown, using dashboard, a collection of related graphics (or tables, or other outputs) that are displayed in a structured way that’s easy to navigate.
  * File - New File - R markdown - From Template - Flex Dashboard
  
```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(p8105.datasets)

data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |>
  select(
    neighbourhood_group, neighbourhood, stars, price, room_type, lat, long) |>
  filter(
    !is.na(stars), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  plot_ly(y = ~price, color = ~neighbourhood, type = 'box', colors = 'viridis')
```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}
nyc_airbnb |> 
  mutate(text_label = str_c("Price: $", price, "\nRating: ", stars)) |> 
  plot_ly(x = ~lat, y = ~long, color = ~price, text = ~text_label,
         type = 'scatter', mode = 'markers', alpha = 0.5)
```

### Chart C

```{r}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood,
          type = 'bar', colors = 'viridis')
```

