---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Plot_ly

we are making interactive plots.

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(plotly)
library(p8105.datasets)
```

focus on NYC Airbnb Data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |>
  select(
    neighbourhood_group, neighbourhood, stars, price, room_type, lat, long) |>
  filter(
    !is.na(stars), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)
```

# let's make a scatterplot!

* the difference between ggplot is:
  * we can zoom, zoom in/out, pan, ... if we want
  * we can know more info of each point in the plot (move the cursor onto each point and the corresponding x and y will be displayed)
    * so this give us a way to look around at things in ds.
    
```{r}
nyc_airbnb |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()

nyc_airbnb |> 
  mutate(text_label = str_c("Price: $", price, "\nRating: ", stars)) |> 
  plot_ly(x = ~lat, y = ~long, color = ~price, text = ~text_label,
         type = 'scatter', mode = 'markers', alpha = 0.5)
```

* for **text**:
  * first, use mutate() to create a variable called "text_label.
    * **str_c()**: join multiple strings into 1 string
    * **\n** is understood to be a line break here - get a line break before "Rating"
    
# let's make a boxplot!

```{r}
nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  plot_ly(y = ~price, color = ~neighbourhood, type = 'box', colors = 'viridis')
```

* what's good for this boxplot:
  * we can see 5 summary info (q1,q2,q3,min,max) directly on the plot when we put cursor onto each bar.
  * on the right part:
    * single click the city to make it go away.
    * double click the city if we exclusively want this city's info.
    * double click a city and then single click other cities, then can make comparison among them b/c only these cities stay.
    
# let's make a bar plot!

```{r}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood,
          type = 'bar', colors = 'viridis')
```
we use count to get the number of rentals in each neighborhood (i.e. to get the bar height).

# ggplotly

You can convert a ggplot object straight to an interactive graphic using ggplotly.

```{r}
ggp_scatter =
  nyc_airbnb |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()

ggplotly(ggp_scatter)
```

* **ggplotly()** is like taking the ggplot and convert it into a plotly plot. But the quality of this graphic is not good. hard to explain. you can do this but in this course do not.